Legacy Data Confounds Modern Genomics Studies

### 2019-06-18 PlottingScripts/ProcessPlotData.Rmd
updated supplementary plots, and legends.

## Mutation Spectrum enrichment
```{r}
#get positions of significant SNPs
sig.pos <- SigPos[,c('Chr','Pos')]
write.table(sig.pos, 
            file=paste0(DataPath,
                        'sig.pos.txt'), 
            col.names = FALSE, 
            row.names = FALSE, 
            quote = FALSE, 
            sep = '\t')

#get positions of random SNPs as control
set.seed(123)
random.pos <- NotSig[sample(nrow(NotSig), 
                            nrow(sig.pos)),
                     c('Chr','Pos')]
write.table(random.pos, 
            file = paste0(DataPath,
                        'random.pos.txt'), 
            col.names = FALSE, 
            row.names = FALSE, 
            quote = FALSE, 
            sep = '\t')
rm(NotSig) #save memory
```
extract context for snps of interest
```{bash}
#Using GenomeWide.AncestralContext.txt
#To get mutation context, use $path/AncestralContext.py
#compare first two columns in both files, extract matches
path='/Users/luke/Documents/QualityPaper/Misc/'
if [ ! -f $path/random.pos.context.txt ]; then
  echo "random pos context"
  awk 'NR==FNR{a[$1,$2];next} ($1,$2) in a' \
  $path/random.pos.txt \
  $path/GenomeWide.AncestralContext.txt \
  > $path/random.pos.context.txt
fi

@@

extract context for GCAT test snps of interest
```{bash}
#Using GenomeWide.AncestralContext.txt
#To get mutation context, use $path/AncestralContext.py
#compare first two columns in both files, extract matches
path='/Users/luke/Documents/LegacyData/LatexManuscript/SupplementaryData/'

if [ ! -f $path/gcat.sig.pos.context.txt ]; then
  echo "sig pos context"
  awk 'NR==FNR{a[$1,$2];next} ($1,$2) in a' \
  $path/Significant_Positions.txt \
  $path/GenomeWide.AncestralContext.txt \
  > $path/gcat.sig.pos.context.txtt
fi 
```

@@

#load SNP context
SNP <- read.table(paste0(DataPath,
                         'sig.pos.context.txt'), 
                sep = '\t', 
                header  = FALSE,
                col.names = contextHeader)
rSNP <- read.table(paste0(DataPath,
                          'random.pos.context.txt'), 
                sep = '\t',
                header = FALSE,
                col.names = contextHeader)

@@

SNP
#save to file
saveRDS(SNP,
            paste0(DataPath,
                   'SNP_Context.rds'))

#save to file
saveRDS(rSNP,
            paste0(DataPath,
                   'rSNP_Context.rds'))
```

>>>>

## Mutation Spectrum enrichment
```{r}
########### JPT 1kGP ###########
#get positions of significant SNPs
sig.pos <- SigPos[,c('Chr','Pos')]
write.table(sig.pos, 
            file=paste0(DataPath,
                        'sig.pos.txt'), 
            col.names = FALSE, 
            row.names = FALSE, 
            quote = FALSE, 
            sep = '\t')

#get positions of random SNPs as control
set.seed(123)
random.pos <- NotSig[sample(nrow(NotSig), 
                            nrow(sig.pos)),
                     c('Chr','Pos')]
write.table(random.pos, 
            file = paste0(DataPath,
                        'random.pos.txt'), 
            col.names = FALSE, 
            row.names = FALSE, 
            quote = FALSE, 
            sep = '\t')
rm(NotSig) #save memory

########### GCAT 1kGP ###########
#see RegressionResults.rmd for Regression

#get positions of random SNPs as control
set.seed(123)

number_of_sig <- 
  nrow(Regression[which(
    Regression$Adjusted_Log10p 
    > -log10(0.01)),])

gcat.random.pos <- 
  Regression[sample(nrow(Regression), 
                    number_of_sig),
             c('Chr','Pos')]

write.table(gcat.random.pos, 
            file = paste0(DataPath,
                        'gcat.random.pos.txt'), 
            col.names = FALSE, 
            row.names = FALSE, 
            quote = FALSE, 
            sep = '\t')

strict_sig <- nrow(RegressionMasked[which(
    RegressionMasked$Adjusted_Log10p 
    > -log10(0.01)),])

strict.gcat.random.pos <- 
  RegressionMasked[sample(nrow(RegressionMasked), 
                    strict_sig),
             c('Chr','Pos')]

write.table(strict.gcat.random.pos, 
            file = paste0(DataPath,
                        'strict.gcat.random.pos.txt'), 
            col.names = FALSE, 
            row.names = FALSE, 
            quote = FALSE, 
            sep = '\t')

strict.gcat.pos <- 
  RegressionMasked[which(
    RegressionMasked$Adjusted_Log10p 
    > -log10(0.01)),
    c('Chr','Pos')]

write.table(strict.gcat.pos, 
            file = paste0(DataPath,
                        'strict.gcat.pos.txt'), 
            col.names = FALSE, 
            row.names = FALSE, 
            quote = FALSE, 
            sep = '\t')

```
extract context for snps of interest
```{bash}
#Using GenomeWide.AncestralContext.txt
#To get mutation context, use $path/AncestralContext.py
#compare first two columns in both files, extract matches
path='/Users/luke/Documents/QualityPaper/Misc/'
if [ ! -f $path/random.pos.context.txt ]; then
  echo "random pos context"
  awk 'NR==FNR{a[$1,$2];next} ($1,$2) in a' \
  $path/random.pos.txt \
  $path/GenomeWide.AncestralContext.txt \
  > $path/random.pos.context.txt
fi

@@

extract context for GCAT test snps of interest
```{bash}
#Using GenomeWide.AncestralContext.txt
#To get mutation context, use $path/AncestralContext.py
#compare first two columns in both files, extract matches
out_path='/Users/luke/Documents/LegacyData/LatexManuscript/SupplementaryData/'
path='/Users/luke/Documents/LegacyData/PlottingScripts/ProcessedData/'

if [ ! -f $path/strict.gcat.random.pos.context.txt ]; then
  echo "gcat random pos context"
  awk 'NR==FNR{a[$1,$2];next} ($1,$2) in a' \
  $path/strict.gcat.random.pos.txt \
  $path/GenomeWide.AncestralContext.txt \
  > $path/strict.gcat.random.pos.context.txt
fi

if [ ! -f $path/strict.gcat.sig.pos.context.txt ]; then
  echo "sig pos context"
  awk 'NR==FNR{a[$1,$2];next} ($1,$2) in a' \
  $path/strict.gcat.pos.txt \
  $path/GenomeWide.AncestralContext.txt \
  > $path/strict.gcat.sig.pos.context.txt
fi 
```

@@

#toggle for all snps or just JPT 1kGP snps
name <- 'strict.gcat.' #'gcat.' # ''

#load SNP context
SNP <- read.table(paste0(DataPath, name,'sig.pos.context.txt'), 
                sep = '\t', 
                header  = FALSE,
                col.names = contextHeader)

rSNP <- read.table(paste0(DataPath, name,
                          'random.pos.context.txt'), 
                sep = '\t',
                header = FALSE,
                col.names = contextHeader)

@@

SNP
#save to file
saveRDS(SNP,
            paste0(DataPath, name,
                   'SNP_Context.rds'))

#save to file
saveRDS(rSNP,
            paste0(DataPath, name,
                   'rSNP_Context.rds'))
```
